Follow-up Samples

### 2016-12-22 submission/manuscript_outline_20161024.Rmd
add a split for the two different models (methods)

***Model Creation***
The Random Forest [@breiman_random_2001] algorithm was used to create the model used for prediction of lesion (adenoma or carcinoma) for the `r length(rownames(good_metaf))` individuals with follow up samples.  The model included data on FIT and the bacterial microbiome. Non-binary data was checked for near zero variance and auto correlation.  Data columns that had near zero variance were removed.  Columns that were correlated with each other over a Spearman correlation coefficient of 0.75 had one of the two columns removed.  This pre-processing was performed with the R package caret (v`r paste(packageVersion("caret"))`).  Optimiation of the mtry hyperparameter as well as data on the best, middle, and worse performance of the model involved taking the `r length(rownames(metaI))` samples and making 100 80/20 (train/test) splits in the data where control and lesion were equally represented in the 80 and 20 split, respectively.  This 80% portion was then split again into an 80/20 split, and run through 20 repeated 10-fold cross validations to optimzie the model's AUC (Area Under the Curve of the Receiver Operator Characteristic).  This resulting model was then tested on the 20% of the data that was originally held out from this overall process.  Once the ideal mtry was found the entire `r length(rownames(metaI))` sample set was used to create the final Random Forest model on which testing on the `r length(rownames(good_metaf))`-person cohort was completed.  The default cutoff of 0.5 was used as the threshold to classify individuals as positive or negative for lesion.

***Analysis Overview***

>>>>

***Lesion Model Creation***
The Random Forest [@breiman_random_2001] algorithm was used to create the model used for prediction of lesion (adenoma or carcinoma) for the `r length(rownames(good_metaf))` individuals with follow up samples.  The model included data on FIT and the bacterial microbiome. Non-binary data was checked for near zero variance and auto correlation.  Data columns that had near zero variance were removed.  Columns that were correlated with each other over a Spearman correlation coefficient of 0.75 had one of the two columns removed.  This pre-processing was performed with the R package caret (v`r paste(packageVersion("caret"))`).  Optimization of the mtry hyperparameter involved taking the samples and making 100 80/20 (train/test) splits in the data where control and lesion were equally represented in the 80 and 20 split, respectively.  This 80% portion was then split again into an 80/20 split, and run through 20 repeated 10-fold cross validations to optimzie the model's AUC (Area Under the Curve of the Receiver Operator Characteristic).  This resulting model was then tested on the 20% of the data that was originally held out from this overall process.  Once the ideal mtry was found the entire `r length(rownames(metaI))` sample set was used to create the final Random Forest model on which testing on the `r length(rownames(good_metaf))`-person cohort was completed.  The default cutoff of 0.5 was used as the threshold to classify individuals as positive or negative for lesion.  The hyperparameter, mtry, defines the number of variables to investigate at each split before a new division of the data is created.

***Initial Follow Up Model Creation***
We also investigated whether a model could be created that could identify before and after surgery samples.  The training set utilized the `r length(rownames(good_metaf))`-person cohort that was previously used for testing of the lesion modeld.  The creation of this model and optimization of the mtry hyperparameter was completed using the same procedure that was used to create the lesion model.

***Analysis Overview***
This
